proof-of-concept_mods

### 2023-11-09 proof-of-concept_mods.Rmd
updates, script to run ohbm results

## QUESTIONS
- effect size for poly(age_days, 3) in gam/gamlss
- z scores instead of centiles!!!!
- Fix age -> diff in male and female variance/intercept

@@

```{r, eval=FALSE}
cent.diffs3 %>%
  pivot_longer(starts_with("diff_"), names_to="pheno", values_to="diff", names_prefix = "diff_") %>%
  ggplot() +
  geom_density(aes(x=diff, fill=pheno)) +
  facet_wrap(~pheno_class) +
  theme(legend.position="none")
```

>>>>

## QUESTIONS
- effect size for poly(age_days, 3) in gam/gamlss
- Fix age -> diff in male and female variance/intercept

@@

```{r, eval=FALSE}
cent.diffs3 %>%
  #dplyr::filter(dataset == "cf.gamlss") %>%
  pivot_longer(starts_with("diff_"), names_to="pheno", values_to="diff", names_prefix = "diff_") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_))) %>%
  ggplot() +
  geom_density(aes(x=diff, fill=dataset), alpha=0.4) +
  facet_wrap(~pheno_cat) +
  theme(legend.position="none")
```
